---
title: "Risk Factor Analysis"
output: 
  html_document:
    keep_md: TRUE
    self_contained: true
required_packages:  ['github://HBGD-UCB/longbowRiskFactors','github://jeremyrcoyle/skimr@vector_types', 'github://tlverse/delayed']
params:
  roles:
    value:
      - exclude
      - strata
      - id
      - W
      - A
      - Y
  data: 
    value: 
      type: 'web'
      uri: 'https://raw.githubusercontent.com/HBGD-UCB/longbowRiskFactors/master/inst/sample_data/birthwt_data.rdata'
  nodes:
    value:
      strata: ['study_id', 'mrace']
      id: ['subjid']
      W: ['apgar1', 'apgar5', 'gagebrth', 'mage', 'meducyrs', 'sexn']
      A: ['parity_cat']
      Y: ['haz01']
  script_params:
    value:
      parallelize:
        input: checkbox
        value: FALSE
      count_A:
        input: checkbox
        value: TRUE
      count_Y:
        input: checkbox
        value: TRUE        
      baseline_level:
        input: 'character'
        value: "[1,2)"
  output_directory:
    value: ''
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message=FALSE, eval.after = 'fig.cap')
options(scipen=999)
```

```{r params, warning=FALSE, message=FALSE}
library(longbowtools)
library(longbowRiskFactors)
library(sl3)
library(tmle3)
library(data.table)
library(stringr)
data <- get_tl_data()
nodes <- get_tl_nodes()
library(future)
tl_params <- get_tl_params()

message(nodes)
message(tl_params)
if(tl_params$parallelize){
  
  workers=availableCores()/2
  plan(multicore, workers=workers)
} else {
  workers = 1
  plan(sequential)
}

if(length(nodes$W)==0){
  nodes$W=NULL
}
```

```{r preprocessing}

# drop strata variables not present in data
nodes$strata <- intersect(nodes$strata, names(data))

# drop missing values
processed <- process_missing(data, nodes,complete_nodes = c("id","strata","A","Y"))
data <- processed$data
nodes <- processed$node_list


# convert character columns to factors
char_to_factor <-function(data){
  classes <- sapply(data,data.class)
  char_cols <- names(classes)[which(classes=="character")]
  set(data, , char_cols, data[,lapply(.SD, as.factor), .SDcols = char_cols])
}

char_to_factor(data)

#define learners
if(length(nodes$W)>0){
  qlib <- make_learner_stack("Lrnr_mean",
                             "Lrnr_glm_fast",
                             list("Lrnr_xgboost", nthread=1))

  glib <- make_learner_stack("Lrnr_mean",
                             list("Lrnr_xgboost", nthread=1))



  # qlib <- glib <- make_learner_stack("Lrnr_mean")
  mn_metalearner <- make_learner(Lrnr_solnp, loss_function = loss_loglik_multinomial, learner_function = metalearner_linear_multinomial)
  qb_metalearner <- make_learner(Lrnr_solnp, loss_function = loss_loglik_binomial, learner_function = metalearner_logistic_binomial)

  metalearner <- make_learner(Lrnr_nnls)
  Q_learner <- make_learner(Lrnr_sl, qlib, qb_metalearner)
  g_learner <- make_learner(Lrnr_sl, glib, mn_metalearner)
} else {
  Q_learner <- make_learner(Lrnr_glm)
  g_learner <- make_learner(Lrnr_mean)
}

learner_list <- list(Y=Q_learner, A=g_learner)

```

## Methods
## Outcome Variable

**Outcome Variable:** `r nodes$Y`

## Predictor Variables

**Intervention Variable:** `r nodes$A`

**Adjustment Set:**

```{r print_adjustment_set, results = "asis"}
if(length(nodes$W)==0){
  cat("unadjusted\n")
} else {
  for(covariate in nodes$W){
    cat(sprintf("* %s\n",covariate))
  }
}
```

## Stratifying Variables

The analysis was stratified on these variable(s):

```{r print_strata_variables, results = "asis"}
for(strata_variable in nodes$strata){
  cat(sprintf("* %s\n",strata_variable))
}

strata <- collapse_strata(data, nodes)

```

## Data Summary
```{r data_summary}
obs_counts <- get_obs_counts(data, nodes, tl_params)
kable(obs_counts)

if(params$output_directory!=""){
  counts_file <- file.path(params$output_directory, "obs_counts.rdata")
  
  save(obs_counts, file=counts_file)
}

```


The following strata were considered:

```{r print_strata, results = "asis"}
strata_levels <- sort(unique(strata$strata_label))
for(stratum in strata_levels){
  cat(sprintf("* %s\n",stratum))
}
```

```{r drop_strata, results = "asis"}
count_cols <- setdiff(names(obs_counts), unlist(nodes))
min_counts <- obs_counts[,list(min_cell=min(unlist(.SD))), .SDcols=count_cols,
                         by=eval(nodes$strata)]

strata <- merge(strata,min_counts, by=nodes$strata)

#todo: this could be a script parameter
cell_cutoff <- 5
dropped_strata <- strata[min_cell < cell_cutoff]

if(nrow(dropped_strata)>0){
  cat("### Dropped Strata\n\nSome strata were dropped due to rare outcomes:\n\n")
  # get strata labels for dropped_strata
  dropped_labels <- strata[dropped_strata, strata_label, on=eval(nodes$strata)]
  dropped_labels <- dropped_labels[!is.na(dropped_labels)]
  
  for(stratum in dropped_labels){
    cat(sprintf("* %s\n",stratum))
  }
  
  #actually drop these strata
  data <- data[!(strata_label%in%dropped_labels)]
  strata <- strata[!(strata_label%in%dropped_labels)]
}

if(nrow(data)==0){
  cat("\n\nALL STRATA DROPPED. JOB FINISHED\n")
  knit_exit()
}
```

## Methods Detail

We're interested in the causal parameters $E[Y_a]$ for all values of $a \in \mathcal{A}$. These parameters represent the mean outcome if, possibly contrary to fact, we intervened to set all units to have $A=a$. Under the randomization and positivity assumptions, these are identified by the statistical parameters $\psi_a=E_W[E_{Y|A,W}(Y|A=a,W)]$.  In addition, we're interested in the mean of $Y$, $E[Y]$ under no intervention (the observed mean). We will estimate these parameters by using SuperLearner to fit the relevant likelihood factors -- $E_{Y|A,W}(Y|A=a,W)$ and $p(A=a|W)$, and then updating our likelihood fit using a joint TMLE.

For unadjusted analyses ($W=\{\}$), initial likelihoods were estimated using Lrnr_glm to estimate the simple $E(Y|A)$ and Lrnr_mean to estimate $p(A)$. For adjusted analyses, a small library containing Lrnr_glmnet, Lrnr_xgboost, and Lrnr_mean was used.

Having estimated these parameters, we will then use the delta method to estimate relative risks and attributable risks relative to a prespecified baseline level of $A$.

todo: add detail about dropping strata with rare outcomes, handling missingness


```{r stratified_tmle, message=FALSE}
baseline_level <- tl_params$baseline_level
if(is.null(baseline_level)||is.na(baseline_level)){
  baseline_level = NULL
}
results <- stratified_tmle(data, nodes, baseline_level, learner_list, strata)
formatted_results <- format_results(results, data, nodes)
```

```{r save_results}
if(params$output_directory!=""){
  results_file <- file.path(params$output_directory, "results.rdata")
  
  save(formatted_results, file=results_file)
}
```


# Results Detail

## Results Plots
```{r plot_tsm, warning=FALSE, message=FALSE}
tsm_plot(formatted_results)
```

```{r plot_rr, warning=FALSE, message=FALSE}
rr_plot(formatted_results)
```

```{r plot_ate, warning=FALSE, message=FALSE}
ate_plot(formatted_results)
```

```{r plot_paf, warning=FALSE, message=FALSE}
paf_plot(formatted_results)
```

```{r plot_par, warning=FALSE, message=FALSE}
par_plot(formatted_results)
```

## Results Table
```{r results_tables, results="asis"}
parameter_types <- unique(formatted_results$type)
for(parameter_type in parameter_types){
  cat(sprintf("\n\n### Parameter: %s\n", parameter_type))
  print_cols <- c(nodes$strata, "intervention_level", "baseline_level", 
                  "estimate", "ci_lower", "ci_upper")
  subset <- formatted_results[type==parameter_type, print_cols, with=FALSE]
  
  k <- kable(subset)
  print(k)
}
```
