# Sensitivity analysis of spline-fitting method {#spline}

---
output:
  pdf_document:
    keep_tex: yes
fontfamily: mathpazo
fontsize: 9pt
---

\raggedright



```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
# source(paste0(here::here(), "/0-config.R"))
# setwd("../../")
# source("0-config.R")
plots <- readRDS("figure-copies/plot objects/rf_spline_objects.RDS")
plots2 <- readRDS("figure-copies/plot objects/rf_spline_sens_objects2.RDS")
plots3 <- readRDS("figure-copies/plot objects/rf_spline_sens_objects3.RDS")
plots4 <- readRDS("figure-copies/plot objects/rf_spline_sens4_objects.RDS")

```


## WLZ, stratified by maternal weight

#### Primary plots

```{r, echo = FALSE, message=F}
i<-1
print(plots[[i]]+ scale_y_continuous(limits=c(-1.2, 0.4), breaks = seq(-1.2, 0.4, 0.2), labels = round(seq(-1.2, 0.4, 0.2),1)))
```

#### Splines fit to all data, naive to study membership

```{r, echo = FALSE, message=F}
print(plots2[[i]])
```

#### Splines fit to random-effect pooled monthly means

```{r, echo = FALSE, message=F}
print(plots3[[i]])
```

#### Random-effects meta-analysis of splines, sensitivity to parameters

```{r, echo = FALSE, message=F}
print(plots4[[i]])
```


## WLZ, stratified by maternal height

#### Primary plots

```{r, echo = FALSE, message=F}
i<-2
print(plots[[i]]+ scale_y_continuous(limits=c(-1.2, 0.4), breaks = seq(-1.2, 0.4, 0.2), labels = round(seq(-1.2, 0.4, 0.2),1)))
```

#### Splines fit to all data, naive to study membership

```{r, echo = FALSE, message=F}
print(plots2[[i]])
```

#### Splines fit to random-effect pooled monthly means

```{r, echo = FALSE, message=F}
print(plots3[[i]])
```

#### Random-effects meta-analysis of splines, sensitivity to parameters

```{r, echo = FALSE, message=F}
print(plots4[[i]])
```








## LAZ, stratified by maternal weight

#### Primary plots

```{r, echo = FALSE, message=F}
i<-3
print(plots[[i]]+ scale_y_continuous(limits=c(-2.2, 0.4), breaks = seq(-2.2, 0.4, 0.2), labels = round(seq(-2.2, 0.4, 0.2),1)))
```

#### Splines fit to all data, naive to study membership

```{r, echo = FALSE, message=F}
print(plots2[[i]])
```

#### Splines fit to random-effect pooled monthly means

```{r, echo = FALSE, message=F}
print(plots3[[i]])
```

#### Random-effects meta-analysis of splines, sensitivity to parameters

```{r, echo = FALSE, message=F}
print(plots4[[i]])
```


## LAZ, stratified by maternal height

#### Primary plots

```{r, echo = FALSE, message=F}
i<-4
print(plots[[i]]+ scale_y_continuous(limits=c(-2.2, 0.4), breaks = seq(-2.2, 0.4, 0.2), labels = round(seq(-2.2, 0.4, 0.2),1)))
```

#### Splines fit to all data, naive to study membership

```{r, echo = FALSE, message=F}
print(plots2[[i]])
```

#### Splines fit to random-effect pooled monthly means

```{r, echo = FALSE, message=F}
print(plots3[[i]])
```

#### Random-effects meta-analysis of splines, sensitivity to parameters

```{r, echo = FALSE, message=F}
print(plots4[[i]])
```














## WLZ, stratified by maternal BMI

#### Primary plots

```{r, echo = FALSE, message=F}
i<-5
print(plots[[i]]+ scale_y_continuous(limits=c(-1.2, 0.4), breaks = seq(-1.2, 0.4, 0.2), labels = round(seq(-1.2, 0.4, 0.2),1)))
```

#### Splines fit to all data, naive to study membership

```{r, echo = FALSE, message=F}
print(plots2[[i]])
```

#### Splines fit to random-effect pooled monthly means

```{r, echo = FALSE, message=F}
print(plots3[[i]])
```

#### Random-effects meta-analysis of splines, sensitivity to parameters

```{r, echo = FALSE, message=F}
print(plots4[[i]])
```


## LAZ, stratified by maternal BMI

#### Primary plots

```{r, echo = FALSE, message=F}
i<-6
print(plots[[i]]+ scale_y_continuous(limits=c(-2.2, 0.4), breaks = seq(-2.2, 0.4, 0.2), labels = round(seq(-2.2, 0.4, 0.2),1)))
```

#### Splines fit to all data, naive to study membership

```{r, echo = FALSE, message=F}
print(plots2[[i]])
```

#### Splines fit to random-effect pooled monthly means

```{r, echo = FALSE, message=F}
print(plots3[[i]])
```

#### Random-effects meta-analysis of splines, sensitivity to parameters

```{r, echo = FALSE, message=F}
print(plots4[[i]])
```


